### 2025-06-22 modern-portfolio-theory.qmd
20250622 - simplify code; add clarifying text

@@

As shown below, the correlation between mean and standard deviation of projected points is positive.
That is, greater expected returns (i.e., mean of projected fantasy points) are associated with greater risk or volatility (i.e., standard deviation of projected fantasy points).
Thus, to obtain a lineup that scores greater fantasy points, it may be necessary to take on greater risk.
Moreover, you would not want take take on more risk for the same number of expected fantasy points; in addition, you would not want to score fewer fantasy points for the same amount of risk [@Hitchings2012].

@@

ggplot2::ggplot(
  data = team_projections,
  aes(
    x = team_sd,
    y = team_mean,
    label = team_name)) +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = team_name)) +
  #geom_text(
  #  hjust = 0,
  #  vjust = 0) +
  #geom_smooth() +
  coord_cartesian(
    xlim = c(NA,NA),
    ylim = c(NA,NA),
    expand = TRUE) +
  labs(
    x = "Standard Deviation of Players' Projected Fantasy Points (Season) Across Sources",
    y = "Mean of Players' Projected Fantasy Points (Season) Across Sources",
    title = "Mean vs Standard Deviation of Players' Projected Fantasy Points"
  ) +
  theme_classic()
```

@@

<https://eng.wealthfront.com/2012/01/17/moneyball-using-modern-portfolio-theory-to-win-your-fantasy-sports-league> [@Hitchings2012; archived at <https://perma.cc/JQ6G-KSRT>]

@@

ggplot2::ggplot(
  data = team_projections2,
  aes(
    x = team_sd,
    y = team_mean,
    label = team_name)) +
  geom_point() +
  ggrepel::geom_text_repel(aes(label = team_name)) +
  #geom_text(
  #  hjust = 0,
  #  vjust = 0) +
  #geom_smooth() +
  coord_cartesian(
    xlim = c(NA,NA),
    ylim = c(NA,NA),
    expand = TRUE) +
  labs(
    x = "Standard Deviation of Players' Fantasy Points From Week-to-Week",
    y = "Mean of Players' Fantasy Points Across Weeks",
    title = "Mean vs Standard Deviation of Players' Projected Fantasy Points"
  ) +
  theme_classic()
```

>>>>

We can examine the efficient frontier of fantasy performance based on the mean and variability of players' projected fantasy points across projection sources.

@@

As shown below, the correlation between mean and standard deviation of projected points is positive.
That is, greater expected returns (i.e., mean of projected fantasy points) are associated with greater risk or volatility (i.e., standard deviation of projected fantasy points).
Thus, to obtain a lineup that scores greater fantasy points, it may be necessary to take on greater risk.
Moreover, you would not want take take on more risk for the same number of expected fantasy points; in addition, you would not want to score fewer fantasy points for the same amount of risk [@Hitchings2012; archived at <https://perma.cc/NE35-G6LR>].

@@

ggplot2::ggplot(
  data = team_projections,
  aes(
    x = team_sd,
    y = team_mean,
    label = team_name)) +
  geom_point() +
  ggrepel::geom_text_repel() +
  labs(
    x = "Standard Deviation of Players' Projected Fantasy Points (Season) Across Sources",
    y = "Mean of Players' Projected Fantasy Points (Season) Across Sources",
    title = "Mean vs Standard Deviation of Players' Projected Fantasy Points"
  ) +
  theme_classic()
```

@@

We can also examine the efficient frontier of fantasy performance based on the mean and variability of players' projected week-to-week fantasy points [@Hitchings2012; archived at <https://perma.cc/JQ6G-KSRT>].

@@

ggplot2::ggplot(
  data = team_projections2,
  aes(
    x = team_sd,
    y = team_mean,
    label = team_name)) +
  geom_point() +
  ggrepel::geom_text_repel() +
  labs(
    x = "Standard Deviation of Players' Fantasy Points From Week-to-Week",
    y = "Mean of Players' Fantasy Points Across Weeks",
    title = "Mean vs Standard Deviation of Players' Projected Fantasy Points"
  ) +
  theme_classic()
```
